### 2017-03-22 main.tex
First mention of a bird name, lny64, is now called out as a bird name.

\begin{figure}
  % Width: 8, Height: 3, Fonts scale: 120%
  \includegraphics[width=\textwidth]{Fig1}
  \caption{The spectrogram of the song of lny64, used as an example
    throughout this paper.  This image was made by superposing the
    spectra of our 2818 aligned songs.  Our example detection points,
    $t^*_1\ldots t^*_6$, are shown as red lines, with example recognition
    regions of 30 ms $\times$ 1--8 kHz marked as rectangles.}
  \label{fig:song}
\end{figure}

@@

We found these parameters to work well across a variety of target
syllables, but various other parameter sets yield results similar to
those presented here.  Some of the parameters trade off detection
accuracy or temporal precision vs.~training time. For example,
decreasing the frame interval generally decreases both latency and
jitter, but also increases training time. Sometimes the effects are
syllable-specific: for example, using a 30-ms time window rather than
50 ms speeds training while usually having a minimal effect on
detector performance (as is the case, for example, for all of the
detection points for lny64), but occasionally a syllable will be seen
for which extending the window to 80 ms is helpful.

>>>>

\begin{figure}
  % Width: 8, Height: 3, Fonts scale: 120%
  \includegraphics[width=\textwidth]{Fig1}
  \caption{The spectrogram of the song of the bird ``lny64'', used as an example
    throughout this paper.  This image was made by superposing the
    spectra of our 2818 aligned songs.  Our example detection points,
    $t^*_1\ldots t^*_6$, are shown as red lines, with example recognition
    regions of 30 ms $\times$ 1--8 kHz marked as rectangles.}
  \label{fig:song}
\end{figure}

@@

We found these parameters to work well across a variety of target
syllables, but various other parameter sets yield results similar to
those presented here.  Some of the parameters trade off detection
accuracy or temporal precision vs.~training time. For example,
decreasing the frame interval generally decreases both latency and
jitter, but also increases training time. Sometimes the effects are
syllable-specific: for example, using a 30-ms time window rather than
50 ms speeds training while usually having a minimal effect on
detector performance (as is the case, for example, for all of the
detection points for the bird ``lny64''), but occasionally a syllable will be seen
for which extending the window to 80 ms is helpful.
